О множествах точек на плоскости с целочисленными расстояниями

### 2019-06-01 pps-linear-bound/pps-linear-lower-bound.tex
A note
A label

In [TODO:cite], TODO: theorem about sublinear quantity of points on the line.
However, we need the values of all the constants in such an estimate.

@@

\begin{conjecture}
	Every set $M\in\mathfrak{M}(2,n)$, $n\geq 6$, such that for some $M_1,M_2$ equality $|M_1 M_2|=1$ holds,
	is not optimal.
\end{conjecture}

>>>>

In [TODO:cite], TODO: theorem about sublinear quantity of points on the line.
However, we need the values of all the constants in such an estimate.
To obtain such values, we will now prove a generalization of~\cite[lemma 3]{our-vmmsh-2018}.

@@

\begin{conjecture}
	\label{con:no_optimal_with_edge_1}
	Every set $M\in\mathfrak{M}(2,n)$, $n\geq 6$, such that for some $M_1,M_2$ equality $|M_1 M_2|=1$ holds,
	is not optimal.
\end{conjecture}
